R tools for accessing research literature for text mining

### 2019-08-23 manuscript.tex
remake pdf

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is
a ``versioned, publicly-editable catalog of research publications:
journal articles, conference proceedings, preprints, blog posts''.
Fatcat is currently does not have an R client, but is used inside of the
\href{https://github.com/ropensci/fulltext}{fulltext} package.

>>>>

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is
a ``versioned, publicly-editable catalog of research publications:
journal articles, conference proceedings, pre-prints, blog posts''.
Fatcat currently does not have an R client, but is used inside of the
\href{https://github.com/ropensci/fulltext}{fulltext} package.
